% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,agenda]{standalone}
% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,chair]{standalone}
\documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false]{standalone}
\newcommand{\meetingType}{general}
\usepackage{groupmeetings}

\begin{document}

\setdate{2016--02--10}
\setpresent{
    \chair{S.~Searles-Bryant},
    % \boardmember{M.~Fry},
    L.~Foglianti Spadini,
    A.~Hyslop,
    A.~Kallaivannan,
    R.~Kent,
    C.~Lau,
    A.~Rutley,
    S.~Wright,
    L.~Yeo
}
\absent{A.~Goodsell \textit{(apologies)}}
\alsopresent{Robert Kane \textit{(Group 4)}, Cameron Voisey \textit{(Group 4)}}

\maketitle

\section{Follow-up from board meeting}
    \begin{items}
    \subsection{Acrylic}
        \item AR looked online and got a quote from Hamar Acrylic Fabrications in Bethnal Green:  \pounds{8} + VAT. Can save on shipping costs by collecting. Quote is for clear; we could have any colour.
        \decisions Go cheap for now with clear.

    \subsection{Electronics box}
        \item SSB: The box in the lab is unsuitable.
        \decisions Get the box from Maplin.
        \item SSB has put switch, grommets, battery box in the cardboard model from last week to check everything fits. It does.

    \subsection{Mid-term review}
        \item SSB has email Prof.~Ford; no reply yet.
        \item CH will ask a group member when their meetings are.

    \subsection{More money}
        \item We should wait until we can make a case with a budget before asking for more.
        \item We have roughly \pounds{30} left.

    \subsection{Caster wheel}
        \item AR: this will cost between \pounds{2.50} and \pounds{5}.

    \subsection{Drawing mechanism}
        \item AR has modified tool to have 3 prongs as discussed.
    \end{items}

\section{New Business}
    \begin{items}
        \item We should produce a plan of manufacture for the robot. (We began to do this in subgroups.)
        \item We should put as much together before next board meeting so we can start to troubleshoot issues.
    \end{items}


\vspace{1em}
\nextmeeting{Board meeting on Tuesday, February 23, at 11:15 in MPEB 3.14a}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Produce plan of manufacture}{all}
    \action{Start manufacture process}{all}
\end{items}

\end{document}
