% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,agenda]{standalone}
% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,chair]{standalone}
\documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false]{standalone}
\newcommand{\meetingType}{general}
\usepackage{groupmeetings}

\begin{document}

\setdate{2016--03--02}
\setpresent{
    \chair{A.~Goodsell},
    \boardmember{M.~Fry},
    L.~Foglianti Spadini,
    A.~Hyslop,
    A.~Kallaivannan,
    R.~Kent,
    C.~Lau,
    A.~Rutley,***
    S.~Searles-Bryant,
    S.~Wright,
    L.~Yeo
}
%\absent{B.~Gone \textit{(sabbatical)}}
%\alsopresent{\boardmember{P.~Bartlett}}

\maketitle



AG concerned about GPS: not getting position. Think somethign to do with sats or weather? Even when getting data, seems slow to update position: certainly too slow for us. We need to test it with moving ASAP. How soon can wetake the robot outside?
Progress: cables still not arrived, we can use the spade terminals
SSB and RK will fix everythign together on Thursday @ 4. We can take it out on Friday to test

AG concerned about drawing mech: where are we with that?
Deadline for building next fri

pin conflict on GPS and motors. easy fix

Next week start editing report







\section{Old business}
\begin{items}
    \item Ratification of minutes from 2016-01-13.
\end{items}
\begin{hiddenitems}
    % \item \priormins
\end{hiddenitems}


\section{Announcements \& progress}
\begin{items}
    \item
\subsection{}

\end{items}


\section{New Business}
\begin{items}
\item
\end{items}

\vspace{1em}
\nextmeeting{Board meeting on Tuesday, January 19, at 11:15 in MPEB 3.14a. General meeting on Wednesday, January 27 at 13:00.}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Make the thing.}{SSB}
\end{items}

\end{document}
