\setdate{2016--01--14}

\setpresent{
    \chair{A.~Goodsell},
    L.~Foglianti Spadini,
    A.~Hyslop,
    A.~Kallaivannan,
    R.~Kent,
    C.~Lau,
    A.~Rutley,
    S.~Searles-Bryant,
    S.~Wright
}

\absent{L.~Yeo \textit{(appologies)}}

\begin{document}
\maketitle

\section{Announcements}
\begin{hiddenitems}
    \item We now have a Whatsapp group for communication.
    \item The project report can be edited on Overleaf at \url{https://www.overleaf.com/4075528rppsqb}.
    \item General team meetings will take place each Wednesday from 1300h (a room will be booked).
\end{hiddenitems}
\subsection{Deadlines and milestones}
\begin{items}
    \item 24/02 mid-term review (1700h)
    \item 18/03 self assessment (1700h)
    \item 21/03 report deadline (1700h)
    \item 20/01 decisions made on design outline
\end{items}

\section{Project decisions}
Decisions marked in \textbf{bold}.
\begin{items}
    \item Scale: tabletop or beach? There is a natural tendency during discussion towards \textbf{beach-size}
    \item Motivation: consensus on \textbf{education} as motivation. Robot programable by children (like a primary school robot); coordinate system; children set start/end points and waypoints and whether or not to draw. Teaches algorithmic thinking (\emph{e.g.} age 6--9).
    \item Robot generated--pattern or user input?
    \begin{itemize}
        \item \textbf{Path planned by user};
        \item RC vehicle (user drives).
    \end{itemize}
    What's more interesting? RC car or \textbf{automated}?
\end{items}

\section{Allocation of roles/responsibilities}
\subsection{Skills and interests}
\begin{items}
    \item RK: fixing stuff together; not big on design; ``if you can measure it I'm okay with it.''
    \item AR: hardware; art review (GCSE art)
    \item SW: a little electronics
    \item CL: like RK; best suited to construction
    \item AH: art review; lit rev. hist robotics; likes lab work so either design or putting together
    \item LFS: software development, design path rather than arduino code
    \item SSB: background in electronics
    \item alex: background in web design; theoretical (software, algorithms)
    \item Arun: help put together; can fill gaps and help out where needed
    \item LY \emph{in absentia}: software
\end{items}
\subsection{Inital research and topic allocations}
\begin{description}
    \item[Art review] Looking into history of sand art; choose type of thing to draw. (AR, AH)
    \item[History of robotics review] Look at movement/digging mech, materials, and history. (SW, AK)
    \item[Education review] Case for teaching children algorithmic thinking; existing ways in which this is achieved. (SSB)
    \item[Design outline] Areas of design which should be decided upon this week.
    \begin{itemize}
        \item Movement (SW, AK)
        \item Interface
        \item Guidance (LFS, CL)
        \item Construction materials (SW, AK)
        \item Digging mechanism (SW, AK)
        \item Electronics platform (CL, SSB)
    \end{itemize}
    \item[Organise lab time] Ask for some time and space to be allocated to our group for practical work (RK)
    \item[Website] Project website (AG, AH)
\end{description}

\vspace{1em}
\nextmeeting{Board meeting on Tuesday, January 19, at 11:15 in MPEB 3.14a. General meeting on Wednesday, January 20 at 11:00.}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Start reviews; preliminary findings by next board meeting}{all}
    \action{Build website so progress can be posted periodically}{AG, AH}
    \action{Organise lab time}{RK}
\end{items}

\end{document}
