% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,agenda]{standalone}
% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,chair]{standalone}
\documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false]{standalone}
\newcommand{\meetingType}{board}
\usepackage{groupmeetings}

\begin{document}

\setdate{2016--03--08}
\setpresent{
    \chair{A.~Goodsell},
    \boardmember{M.~Fry},
    A.~Hyslop,
    A.~Kallaivannan,
    C.~Lau,
    A.~Rutley,
    S.~Searles-Bryant,
    S.~Wright,
    L.~Yeo
}
\absent{L.~Foglianti Spadini \textit{(apologies)},
R.~Kent \textit{(apologies)}
}
% \alsopresent{\boardmember{P.~Bartlett}}

\maketitle
% \centering {Malet Place Engineering Building, room 3.14a}
\section{Old business \& announcements}
\begin{items}
    % \item Ratification of minutes from 2016--02--23.
    \item \priormins
    \item The website has been updated.
\end{items}

\section{Progress \& discussion}
\begin{items}
    \subsection{\SandE moves!}
        \item We have made \SandE drive! (We have videos.)
        \item The robot is currently not stable: it doesn't turn on a curve properly and cannot drive in a straight line. The axles aren't parallel and the wheels are slipping on the axles (they are not fixed together by anything but friction). We need to replace the axles; new wheels are begin delivered today.\\
        MF suggests a grub screw on the wheel and a flattened section (filed) on the axle to fix the wheel in place.
        \item We had sketches to draw a square using GPS coordinates. The sketch did not run as expected; we believe that we need the compass to determine the robot's bearing whilst stationary.\\
        SW: we should test individual subsystems before trying to combine them.
        \item MF suggests attaching chalk to the drawing mechanism to test the robot on land (in the Quad).
    \subsection{Drawing mechanism}
        \item AR has found some servo mounts on eBay which we can have before the end of the week.
        \item The rakes can be 3d printed; AR will design these so SSB can get them printed in the Institute of Making (in the UV resin printers).
    \subsection{Money}
        \item AG has asked for more money. We have not yet had a response.
\end{items}

\section{New Business}
\begin{items}
    \subsection{Final report}
        \item For the next few days, our priority should be writing the report.
        \item We should begin editing the report this week. SSB, SW, and AH will start editing the report at the end of the week.
        \item It will cost c. \pounds{12.50} to be printed (in greyscale) and bound (150 pages, 7p per page + approx. \pounds{2} for binding). We can split this cost between us.
        \item MF asks that the report contains a matrix of what
    \subsection{Poster presentation}
        \item Will need to be ``A0 and of a form that would be accepted for a scientific conference.''
        \item We need to determine how it will be printed and who will pay.
        \item AR, AH, and AK will start to design the poster.
        \item Datasheets can be included in an annex if they are short.
\end{items}

\vspace{1em}
\nextmeeting{Tuesday, March 15, at 11:15 in MPEB 3.14a}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Write the report}{all}
    \action{Begin editing the report}{SSB, SW, AH}
    \action{Begin designing the poster}{AR, AH, AK}
\end{items}

\end{document}
