% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,agenda]{standalone}
% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,chair]{standalone}
\documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false]{standalone}
\newcommand{\meetingType}{general}
\usepackage{groupmeetings}

\begin{document}

\setdate{2016--01--20}
\setpresent{
    \chair{A.~Goodsell},
    \boardmember{M.~Fry},
    L.~Foglianti Spadini,
    A.~Hyslop,
    A.~Kallaivannan,
    R.~Kent,
    C.~Lau,
    A.~Rutley,
    S.~Searles-Bryant,
    S.~Wright,
    L.~Yeo
}
%\absent{B.~Gone \textit{(sabbatical)}}
%\alsopresent{\boardmember{P.~Bartlett}}

\maketitle

\section{Announcements}
\begin{items}
    \item We do not have access to our space in Lab 3 on Tuesdays unless we make special arrangements. We also only have half a bench.
\end{items}

\section{Old business}
\begin{items}
    \item \priormins
\end{items}


\section{Design specification}
\begin{items}
    \item \textsc{Decision}: The robot will use GPS for guidance.
    \item \textsc{Decision}: The robot will be controlled with an Arduino.
    \item Design specification researched:
    \begin{subitems}
        \item \writers{AH, SW, LY} Health and safety re: children around electronics;
        \item \writers{AG, AR} Nearby beaches;
        \item \writers{RK, LFS, CL} Health and safety re: electronics \& water.
        \item \writers{SSB} Precision of GPS
    \end{subitems}
    \item Design specification started
\subsection{Division of team}
    \item Three teams:
    \begin{subitems}
        \item Electronics: SSB, SW, AH
        \item Hardware: CL, RK, AR, AK
        \item Software: LY, LFS, AG
    \end{subitems}
\subsection{Tasks}
    \item Hardware
    \begin{subitems}
        \item Design chassis;
        \item choose construction materials;
        \item design drawing tool;
        \item choose method of prototyping.
    \end{subitems}
    \item Software:
    \begin{subitems}
        \item Familiarize with Arduino language and environment;
        \item purchase development board.
    \end{subitems}
    \item Electronics:
    \begin{subitems}
        \item Investigate actuators and motors;
        \item compile list of components;
        \item purchase necessary electronics and acquire other components;
        \item decide on interface with software.
    \end{subitems}
\end{items}

\vspace{1em}
\nextmeeting{Board meeting on Tuesday, January 26, at 11:15 in MPEB 3.14a. General meeting on Wednesday, January 27 at 13:00.}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Confirm precision of civilian GPS measurements.}{SSB}
    \action{Design the robot}{Hardware subgroup}
    \action{Design electronics system}{Electronics subgroup}
    \action{Acquire components}{Electronics subgroup}
    \action{Purchase Arduino and play with it}{Software subgroup}
\end{items}

\end{document}
