% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,agenda]{standalone}
% \documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false,chair]{standalone}
\documentclass[a4paper,11pt,twoside,class=meetingmins,crop=false]{standalone}
\newcommand{\meetingType}{board}
\usepackage{groupmeetings}

\begin{document}

\setdate{2016--02--23}
\setpresent{
    \chair{A.~Goodsell},
    \boardmember{M.~Fry},
    L.~Foglianti Spadini,
    A.~Hyslop,
    A.~Kallaivannan,
    R.~Kent,
    C.~Lau,
    A.~Rutley,
    S.~Searles-Bryant,
    S.~Wright,
    L.~Yeo
}
% \absent{ \textit{(apologies)}}
% \alsopresent{\boardmember{P.~Bartlett}}

\maketitle
% \centering {Malet Place Engineering Building, room 3.14a}
\section{Old business \& announcements}
\begin{items}
    % \item Ratification of minutes from 2016--02--02.
    \item \priormins
\end{items}

\section{Progress \& discussion}
\begin{items}
    \subsection{Mid-term review}
        \item Discussion of notes from interviews of Group 6.\\
        SW and LFS will write up.
    \subsection{Hardware}
        \item AR has fixed some problems with the robot.
        \item AR, CL, RK have attached the motors and wheels to the chassis. We will need new wheels eventually (AR has asked for spare wheels).
        \item The wheels can be cut down to make the robot more compact.
    \subsection{Electronics}
        \item SSB has cut holes in the housing and installed the components.\\
        One cable still has not been delivered so we were waiting on that. If it hasn't arrived yet then SSB will replace the connectors with spade terminals.
    \subsection{Software}
        \item LFS: An algorithm is needed to determine the wheel turning
        \item Discussion of turning on the spot v.~ turning whilst driving
        \item The GPS shield does not appear to be working at all: it is not receiving any signal. AG will try to get it replaced to confirm a problem with the hardware.
        \item LY has written code for turning but makes assumptions (\eg flat ground).\\
        AG points out slow motor speeds, while initially concerning, will help to avoid slipping.
        \item AG: The time constraint on the project means we do not expect to create a UI for children, but can design the software as if it will. MFS and SW point out that the UI can be part of a future project.
\end{items}

\section{New Business}
\begin{items}
    \section{Report}
        \item Everything sent to SSB will be put into the report.
        \item We will aim to have the report finished the weekend before the deadline. We will assign a group to edit the report nearer the deadline.
\end{items}

\vspace{1em}
\nextmeeting{Tuesday, March 8, at 11:15 in MPEB 3.14a}
\vspace{1em}

\section{Actions}
\begin{items}
    \action{Write up mid-term assessment of Group 6}{SW, LFS}
    \action{Replace GPS module}{AG}
\end{items}

\end{document}
